Learning causal features with double regression

### 2019-04-26 paper/paper.tex
roc auc test notebook, and diagonal non zero element test in paper.tex

\subsection{Problem formulation, asymptotic estimates}

Our problem may be formulated as
\begin{equation}
    Y = F(EX + N)
    \label{eq:model}
\end{equation}
where F is an unknown matrix, presumably full or high rank, corresponding to the measurement apparatus, E is a low rank transformation carried on the features (X), and N a noise term, centred but not necessarily gaussian or diagonal.

@@

(here be statistical test for the diagonal, and rationale for it)

@@

>>>>

\subsection{Model formulation, average behaviour}

Our problem may be formulated as
\begin{equation}
    Y = F(EX + N)
    \label{eq:model}
\end{equation}
where F is an unknown matrix, presumably full or high rank, corresponding to the measurement apparatus, E is a low rank transformation carried on the ftkvdkkdtgbcifnndifftgetecfdbjujjeatures (X), and N a noise term, centred but not necessarily gaussian or diagonal.

@@

@@

\subsection{Double regression as feature extraction}

Testing for non zero elements on the diagonal of (9) can be viewed as a one dimensional binary clustering problem: classify n positive real values as "large" and "small" (under the hypothesis that they are not all small or all large). This can be done on maximising the ratio of inter-group variance over total variance (ie minimising intra-group variance). In a one dimensional two clusters setting, this amounts to sorting the data, and separating the p smallest from the n-p largest values so that inter group inertia is maximal.

If s and r are the average values of the two clusters, and p and n-p their size, we are maximising 
\begin{equation}
\begin{aligned}
{p (n-p)\over n^2} (s-r)^2 
\end{aligned}
\end{equation}
 and selecting the p features corresponding to the largest values.
